Technical Report

### 2018-06-22 fully-abstract-comp/technical-report.tex
Refactor, simplify a proof.

\begin{lemma}
  \label{lem:codereg-not-read-write}
  If
  \begin{itemize}
  \item $n > 0$
  \item $\dom(\code) \subseteq \ta$
  \item $\gc =
    (\ta,\stkb,\gsigrets,\gsigcloss)$
  \item $\pwheap(r_\code) \nequal
    \codereg{\sigrets,\sigcloss,\code,\gc}$ 
  \item $a \in \dom(\code)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$
  \end{itemize}
  then
  \begin{itemize}
  \item $\npair{\{a\}} \not\in \readCond{\normal,W}$
    % \item $\npair{\{a\}} \not\in \writeCond{\normal,W}$
    % It seems unnecessary to show the part about the write condition as all non-no-perm permissions have read.
  \end{itemize}
\end{lemma}
\begin{proof}
  For the sake of contradiction assume $\npair{\{a\}} \in \readCond{\normal,W}$.
  Then there exists $S \subseteq \addressable{\lin, \pwheap}$ and $R : S \fun
  \powerset{\nats}$ such that
  \begin{itemize}
  \item $\biguplus_{r\in S} R(r) \supseteq A$
  \item $\forall r \in S \ldotp \pwheap(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$
  \end{itemize}
  Because we know $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$, it must be possible to split up $\ms_S$ in disjoint memory segments that each (paired with a target memory segment) satisfies exactly one region.
  This means that only one region can govern address $a$, so that $r_\code \in S$

  It follows that $R(r_\code) = \dom(\code)$ and $\pwheap(r_\code).H \nsubeq \stdreg{\dom(\code),\gc}{\pur}.H$.
  From the fact that $\npair{(\code,\code)} \in \pwheap(r_\code).H~W'$ for some $W'$ with $W = W' \oplus \_$, and the fact that $\dom(\code)\subseteq \ta$, it also follows that $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$ and $\sigrets,\sigcloss\vdash_{\mathrm{comp-code}} \var{code}$.
  This now gives us a contradiction with Lemma~\ref{lem:codereg-H-not-subs-lrv}.
\end{proof}

@@

>>>>

@@

\begin{lemma}
  \label{lem:codereg-not-read-write}
  If
  \begin{itemize}
  \item $n > 0$
  \item $\dom(\code) \subseteq \ta$
  \item $\gc =
    (\ta,\stkb,\gsigrets,\gsigcloss)$
  \item $\pwheap(r_\code) \nequal
    \codereg{\sigrets,\sigcloss,\code,\gc}$
  \item $a \in \dom(\code)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$
  \end{itemize}
  then
  \begin{itemize}
  \item $\npair{\{a\}} \not\in \readCond{\normal,W}$
    % \item $\npair{\{a\}} \not\in \writeCond{\normal,W}$
    % It seems unnecessary to show the part about the write condition as all non-no-perm permissions have read.
  \end{itemize}
\end{lemma}
\begin{proof}
  For the sake of contradiction assume $\npair{\{a\}} \in \readCond{\normal,W}$.
  Then there exists $S \subseteq \addressable{\lin, \pwheap}$ and $R : S \fun
  \powerset{\nats}$ such that
  \begin{itemize}
  \item $\biguplus_{r\in S} R(r) \supseteq A$
  \item $\forall r \in S \ldotp \pwheap(r).H \nsubeq \stdreg{R(r),\gc}{\pur}.H$
  \end{itemize}
  Because we know $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$, it must be possible to split up $\ms_S$ in disjoint memory segments that each (paired with a target memory segment) satisfies exactly one region.
  This means that only one region can govern address $a$, so that $r_\code \in S$
  It follows that $R(r_\code) = \dom(\code)$ and $\pwheap(r_\code).H \nsubeq \stdreg{\dom(\code),\gc}{\pur}.H$.

  Lemma~\ref{lem:code-reg-and-mem-sat} tells us that $\npair{(\code,\code)} \in \pwheap(r_\code).H~W'$ for some $W'$ with $W = W' \oplus \_$.
  Together with the fact that $\dom(\code)\subseteq \ta$, it then follows that $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$ and $\sigrets,\sigcloss\vdash_{\mathrm{comp-code}} \var{code}$.
  This now gives us a contradiction with Lemma~\ref{lem:codereg-H-not-subs-lrv}.
\end{proof}
